\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
doc/paper.tex: add a little Zurückhaltung
fix two typos

It is important to note that in the case of such problem points it is
non-trivial to judge whether this is because there is no physical
solution for the given parameter space point or whether a solution
exists but the fixed point iteration is unable to find the solution.
While \fs makes it as easy as possible to fin spectra, when studying
new models a physical understanding of the model is still essential
and this can help the user determine why the such problems arise.

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY model file, such
as changing the choice of \code{HighScaleFirstGuess} or altering
\code{HighScaleMinimum} and \code{HighScaleMaximum} which can be used
to push the iteration back towards where the solution should be if it
gets off track.For experienced users the clear code structure also allows the
possibility of direct adaption of the code.

Finally instead of tinkering with the two-scale solver one may wish to
replace it entirely. The modular design of FlexibleSUSY allows for the
solver for the boundary value problem to be replaced. An alternative
solver with better convergence properties (at the expense of slower
speed) is already planned for a later release.

>>>>

It is important to note that in the case of such problem points it is
non-trivial to judge whether this is because there is no physical
solution for the given parameter space point or whether a solution
exists but the fixed point iteration is unable to find the solution.
While \fs makes it as easy as possible to find spectra, when studying
new models a physical understanding of the model is still essential
and this can help the user determine why the such problems arise.

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY model file, such
as changing the choice of \code{HighScaleFirstGuess} or altering
\code{HighScaleMinimum} and \code{HighScaleMaximum} which can be used
to push the iteration back towards where the solution should be if it
gets off track. For experienced users the clear code structure also allows the
possibility of direct adaption of the code.

Finally instead of tinkering with the two-scale solver one may wish to
replace it entirely. The modular design of FlexibleSUSY allows for the
solver for the boundary value problem to be replaced. An alternative
solver with potentially better convergence properties (at the expense of slower
speed) is already planned for a later release.
